A new model to predict survival in patients with end-stage liver disease

### 2022-07-18 analysis/article.Rmd
refactor: restruct headings
refactor: reorder keywords
refactor: move data and software availability section
refactor: labm requires upper case litre

  **Keywords**:
      end-stage liver disease; MELD; risk stratification; machine learning;
      survival estimation; IL-6.

@@

MELD and MELD-Na were calculated as described in
@optn_policies2021 using the following formulas:
$MELD = 10 * (0.957 \ln(creatinine [mg/dl]) + 0.378 \ln(bilirubin [mg/dl]) + 1.120 * \ln(INR) + 0.643)$,
Creatinine, bilirubin and INR values lower than 1.0 mg/dl were set to 1.0 mg/dl.
The maximum allowed creatinine was 4.0 mg/dl. If patients received dialysis,
creatinine was set to 4.0 mg/dl.
For MELD-Na MELD was calculated as above and recalculated if greater than 11 using:
$MELD\text{-}Na = MELD_i + 1.32 * (137 - Na [mmol/l]) - (0.033 * MELD_i * (137 - Na [mmol/l]))$

Serum sodium values lower than 125 mmol/l or higher than 137 mmol/l were set
to 125 mmol/l and 137 mmol/l, respectively.

The MELD-Plus7 risk score was calculated as described in @kartoun2017:
$$
\begin{aligned}
L = 8.53499496 &+ \\
    2.59679650 &* \log_{10}(1 + creatinine [mg/dl]) + \\
    2.06503238 &* \log_{10}(1 + bilirubin [mg/dl]) + \\
    2.99724802 &* \log_{10}(1 + INR) - \\
    6.47834101 &* \log_{10}(1 + sodium [mmol/l]) - \\
    6.34990436 &* \log_{10}(1 + albumin [g/l]) + \\
    1.92811726 &* \log_{10}(1 + wbc [th/cumm]) + \\
    0.04070442 &* age [years]
\end{aligned}
$$

@@

## Conclusion

@@

# Data and software availability

# Acknowledgement

@@

# Research funding

@@

# Author contributions

@@

# Competing interests

@@

# Informed consent

@@

# Ethical approval

@@

>>>>

  **Keywords**:
      end-stage liver disease; IL-6; machine learning; MELD;
      risk stratification; survival estimation.

@@

MELD and MELD-Na were calculated as described in
@optn_policies2021 using the following formulas:
$MELD = 10 * (0.957 \ln(creatinine [mg/dL]) + 0.378 \ln(bilirubin [mg/dL]) + 1.120 * \ln(INR) + 0.643)$,
Creatinine, bilirubin and INR values lower than 1.0 mg/dL were set to 1.0 mg/dL.
The maximum allowed creatinine was 4.0 mg/dL. If patients received dialysis,
creatinine was set to 4.0 mg/dL.
For MELD-Na MELD was calculated as above and recalculated if greater than 11 using:
$MELD\text{-}Na = MELD_i + 1.32 * (137 - Na [mmol/L]) - (0.033 * MELD_i * (137 - Na [mmol/L]))$

Serum sodium values lower than 125 mmol/L or higher than 137 mmol/L were set
to 125 mmol/L and 137 mmol/L, respectively.

The MELD-Plus7 risk score was calculated as described in @kartoun2017:
$$
\begin{aligned}
L = 8.53499496 &+ \\
    2.59679650 &* \log_{10}(1 + creatinine [mg/dL]) + \\
    2.06503238 &* \log_{10}(1 + bilirubin [mg/dL]) + \\
    2.99724802 &* \log_{10}(1 + INR) - \\
    6.47834101 &* \log_{10}(1 + sodium [mmol/L]) - \\
    6.34990436 &* \log_{10}(1 + albumin [g/L]) + \\
    1.92811726 &* \log_{10}(1 + wbc [th/cumm]) + \\
    0.04070442 &* age [years]
\end{aligned}
$$

@@

# Conclusion

@@

## Acknowledgement

@@

## Research funding

@@

## Author contributions

@@

## Competing interests

@@

## Informed consent

@@

## Ethical approval

@@

## Data and software availability
